Drake Plan

### 2019-08-29 R/drake_plan_conus.Rmd
add set.seed

# point to cache: 
ssd_cache = drake_cache(path = "/scratch/cache/aeronet_drake") 
```

@@

# Allowing `add_hist` in `plot_scatter` (or use plotly) requires set lock_envir to FALSE:
make(conus_plan_cv, cache = ssd_cache, lock_envir = FALSE)

```

>>>>

# point to cache: 
ssd_cache = drake_cache(path = "/scratch/cache/aeronet_drake")
set.seed(1234)
```

@@

# Allowing `add_hist` in `plot_scatter` (or use plotly) requires set lock_envir to FALSE:
make(conus_plan_cv, cache = ssd_cache, lock_envir = FALSE)
```
